---
title: "largest cities"
author: "David Phillips"
date: '2022-09-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Write down the name of a country and its largest city, one after the other. Hidden in this string, in consecutive letters, is another country's capital (in six letters)? What is it?
The first country's capital and the second country's largest city share the same two starting letters.

Edit: Islamabad and Istanbul.
A: PakistAN KARAchi --> ANKARA (Turkey)

```{r cars}
library(rvest)
url <- "https://kids.kiddle.co/List_of_countries_by_largest_and_second_largest_cities"
country_largest <- url %>%
  read_html() %>%
  html_nodes(xpath='/html/body/div/div/div[2]/div[3]/div[1]/table') %>%
  html_table()
country_largest <- country_largest[[1]]


#clean up a bit 

country_largest<-country_largest[4:nrow(country_largest),c(1:2)]

country_largest[1:2] <-
  lapply(country_largest[1:2], stringr::str_to_upper)

country_largest$combined <-
  paste0(country_largest$`Country or territory`,
         country_largest$`City proper`)

names(country_largest) <- c("country", "city", "combined")

```

## Captals 

```{r}



url <- "https://en.wikipedia.org/wiki/List_of_national_capitals"
capitals <- url %>%
  read_html() %>%
  html_nodes(xpath = '/html/body/div[3]/div[3]/div[5]/div[1]/table[2]') %>%
  html_table()
capitals <- capitals[[1]][, 1]

capitals <- stringr::str_extract(capitals$`City/Town`, "[^(]+")

capitals <- trimws(capitals)

capitals <- stringr::str_to_upper(capitals)

#country_largest$detected<-stringr::str_extract(country_largest$combined,capitals)


solution_df <-
  do.call(rbind, lapply(1:nrow(country_largest), function(x) {
    out <-
      unique(stringr::str_extract(country_largest[x, ]$combined, capitals))
    if (length(out) > 1) {
      out <- out[(!is.na(out))]
    }
    final <- data.frame(country_largest[x, ], out)
    if (final$out != final$city & !is.na(final$out)) {
      return(final)
    }
  }))



```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
